%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{natbib}
%\usepackage[sorting=ydnt]{biblatex}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}


\begin{center}
    {\Huge \scshape Fernando I. Alvarez-Santana} \\ \vspace{1pt}
    Ensenada, B.C. México. \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 646-286-91-66 ~ \href{mailto:ferwazz93@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ferwazz93@gmail.com}} ~ 
    \href{https://linkedin.com/in/fernando-alvarez-santana-6a4234133/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/fernando-alvarez-santana-6a4234133}}\\ \vspace{1pt}
    \href{https://github.com/islasfernando}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/islasfernando}}
    \href{https://github.com/ferwazz}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/ferwazz}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad Autónoma de Baja California (UABC)}{Ago. 2012 -- Jun 2017}
      {Bachelor in Physics}{Ensenada, B.C.}\\ \vspace{15pt}
    \resumeSubheading
      {Instituto de astronomía (IA-UNAM)}{Ago. 2017 -- Oct 2020}
      {Master in Astrophysics}{Ensenada, B.C.}\\ \vspace{10pt}      
      \textbf{Thesis:} \textit{Methodology for the identification of exoplanet transit candidates in high cadence photometry data}\\ \vspace{3pt}
        In this project I worked with high cadence (20 frames per second) observational photometric 
        data of exoplanet transits events. The data was obtained by me at the National
        Astronomical Observatory (OAN-SPM) using the 0.84m telescope, in order to prepare a pipeline for the automatic recognition of possible
        exoplanet candidates that may be observed by the \href{http://taos2.astrosen.unam.mx/}{\underline{TAOS-2}} project.
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Grupo de Ecología y Conservación de Islas. A.C. (GECI)}{May 2019 -- Present}
      {Specialist in data analysis and machine learning}{Ensenada, B.C.}\\ \vspace{7pt}
      \small Some details are confidential due to non-disclosure agreements.
      \resumeItemListStart
        \resumeItem{Work with python to implement reproducible machine learning algorithms or statistical analysis for the scientific use of data collected by the organization.}
        \resumeItem{\href{https://github.com/IslasGECI/nerd}{\raisebox{-0.2\height}\faGithub\ \underline{NERD}}: Migrate MATLAB code to python and add mutation testing.}
        \resumeItem{\href{https://github.com/IslasGECI/cormorant_population_growth}{\raisebox{-0.2\height}\faGithub\ \underline{Cormorant Population}}: Reprodubible scientific report, fit a population model to a bootstrapped time series data to estimate the population trend.}
        \resumeItem{Data driven desicision making. Measure the impact of our flora and fauna conservations actions, presenting models results using data visualizations and technical reports.}

      \resumeItemListEnd

    \resumeSubheading
      {UABC}{Feb 2018 -- May 2019}
      {Teacher}{Ensenada, B.C.} \vspace{3pt}
      \resumeItemListStart Courses:
        \resumeItem{Laboratory of thermodynamics,  and electrical circuits.}
        \resumeItem{laboratory of electricity and magnetism.}
        \resumeItem{Electrical circuits}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, JavaScript} \\
     \textbf{Packages}{: pandas, scipy, scikit-learn, tensorflow, pymc3, pytorch, D3, Chartjs} \\
     \textbf{Developer Tools}{: VS Code, Jupyter, Azure, Tableau} \\
     \textbf{Technologies/Frameworks}{: Linux, GitHub, Docker, Mutation Testing, Kanban, CI/CD} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Colaborations}
    \nocite{*}
    \begingroup
    \renewcommand{\section}[2]{}%
    \bibliography{CV}
    \bibliographystyle{apalike}
    \endgroup

















    
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gym Reservation Bot} $|$ \emph{Python, Selenium, Google Cloud Console}}{January 2021}
          \resumeItemListStart
            \resumeItem{Developed an automatic bot using Python and Google Cloud Console to register myself for a timeslot at my school gym.}
            \resumeItem{Implemented Selenium to create an instance of Chrome in order to interact with the correct elements of the web page.}
            \resumeItem{Created a Linux virtual machine to run on Google Cloud so that the program is able to run everyday from the cloud.}
            \resumeItem{Used Cron to schedule the program to execute automatically at 11 AM every morning so a reservation is made for me.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Ticket Price Calculator App} $|$ \emph{Java, Android Studio}}{November 2020}
          \resumeItemListStart
            \resumeItem{Created an Android application using Java and Android Studio to calculate ticket prices for trips to museums in NYC.}
            \resumeItem{Processed user inputted information in the back-end of the app to return a subtotal price based on the tickets selected.}
            \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Transaction Management GUI} $|$ \emph{Java, Eclipse, JavaFX}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed a sample banking transaction system using Java to simulate the common functions of using a bank account.}
            \resumeItem{Used JavaFX to create a GUI that supports actions such as creating an account, deposit, withdraw, list all acounts, etc.}
            \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
            \resumeItemListStart
                \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
                \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
                \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
